The Way Forward in Parallelizing Dynamic Languages

### 2014-05-02 talk/icooolps2014/position-paper.tex
remove example citation
typo
add something about automatic barrier placement

@@

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
  P. Q. Smith, and X. Y. Jones. ...reference text...

@@

\bibitem{nicholas06}
  Nicholas Riley and Craig Zilles. 2006. Hardware tansactional memory
  support for lightweight dynamic language evolution. \emph{In
    Companion to the 21st ACM SIGPLAN symposium on Object-oriented
    programming systems, languages, and applications} (OOPSLA
  '06). ACM, New York, NY, USA

@@

>>>>

While one can argue that STM requires the insertion of read and write
barriers in the whole program, this can be done automatically and
locally by a program transformation\cite{felber07}. There are attempts
to do the same for fine-grained locking\cite{bill06} but they require
a whole program analysis since locks are inherently non-composable.
The effectiveness of these approaches still has to be proven for our
use case.

@@

@@

\bibitem{nicholas06}
  Nicholas Riley and Craig Zilles. 2006. Hardware transactional memory
  support for lightweight dynamic language evolution. \emph{In
    Companion to the 21st ACM SIGPLAN symposium on Object-oriented
    programming systems, languages, and applications} (OOPSLA
  '06). ACM, New York, NY, USA

@@

\bibitem{felber07}
  Felber, Pascal, et al. "Transactifying applications using an open
  compiler framework." \emph{TRANSACT}, August (2007): 4-6.

\bibitem{bill06}
  Bill McCloskey, Feng Zhou, David Gay, and Eric
  Brewer. 2006. Autolocker: synchronization inference for atomic
  sections. \emph{In Conference record of the 33rd ACM SIGPLAN-SIGACT
  symposium on Principles of programming languages (POPL '06)}. ACM,
  New York, NY, USA
